Experiments with Synthetic Data

### 2022-07-12 dev/notebooks/synthetic.qmd
bleh

```{julia}
include("src/AlgorithmicRecourseDynamics.jl")
using CounterfactualExplanations, Flux, Plots, PlotThemes, Random, LaplaceRedux, LinearAlgebra
theme(:wong)
output_path = output_dir("synthetic")
www_path = www_dir("synthetic")
```

>>>>

```{julia}
include("dev/utils.jl")
using CounterfactualExplanations, Flux, Plots, PlotThemes, Random, LaplaceRedux, LinearAlgebra
theme(:wong)
output_path = output_dir("synthetic")
www_path = www_dir("synthetic")
```
